The Astropy Project

### 2017-11-12 main.tex
nddata

\subsection{Data arrays}

@@

The \package{astropy.nddata} supackage provides three types of functionality:
an abstract interface for representing generic arbitrary-dimensional datasets
intended primarily for developers of other packages, concrete classes
building on this interface and utilities for manipulating these kind of
datasets.

The \texttt{NDDataBase} class provides the abstract interface for gridded data with attributes for accessing metadata, the world-coordinate system (WCS), uncertainty and other traits. Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays. These classes serve as useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.

>>>>

\subsection{Data containers}

@@

The \package{astropy.nddata} supackage provides three types of functionality: an
abstract interface for representing generic arbitrary-dimensional datasets
intended primarily for subclassing by developers of other packages, concrete
classes building on this interface, and utilities for manipulating these kind of
datasets.

The \texttt{NDDataBase} class provides the abstract interface for gridded data
with attributes for accessing metadata, the world-coordinate system (WCS),
uncertainty arrays matched to the data shape, and other traits.
Building on this interface the \texttt{NDData} class provides a minimally working implementation for storing NumPy arrays. These classes serve as useful base for package authors wishing to develop their own classes for specific use cases and as containers for exchanging gridded data.
